A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-15 EvoPar2017/paper.tex
Reviewed section 5

In order to have enough data to perform more analysis on it, a new
experiment was performed along several days with, eventually, several
hundreds of persons participating on it. It was announced by several
popular Twitter figures and found its way into Reddit. The number of
PUTs per minute are shown in \ref{fig:minute}. Sudden peaks in them
are due to new announcements in social networks, usually; this is one
of the problems with this kind of volunteer computing systems: they
feed on the continuous influx of new users; however, this can be
automatized and also encouraged, and, as shown, once enough users have
participated it is sometimes easier to find new ones.

In Figure \ref{fig:minute} check
also the dot color, which 
corresponds to the {\em ratio} or, as indicated above, the actual
number of contributing PUTs, those that have not been discarded due to
repeated sending by clients or (briefly) belonging to the previous
instance of the experiment. It reveals that, in some cases where the
amount of PUTs really increases, they are actually not contributing so
much, while light dots, corresponding to a ration close to 1, usually
stay in the lowest part of the graphic. 
%
\begin{figure}[ht!b]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/entropy-1}

@@

This is interesting in the sense that in indicates that there might be
something more to performance that just the number of volunteers
contributing. In this experiment we include an additional measure:
user-contribution entropy, which is measure by computing the
compression entropy of the user contributions every for the whole
experiment.  This is computed converting the sequence of the number of
PUTs into a string and then compressing it using {\tt Zlib}, a
standard compression library. Since the compression rate is related to
the randomness of the sequence, a higher compression rate will
correspond to an experiment with a low entropy, while a lower
compression rate will indicate that there has been a certain amount of
unexpected changes during the experiment. Although less popular than
Jenssen-Shannon entropy, this way of measuring it is widely used
\cite{ornstein1993entropy} in case where we want to compute the
entropy of sequences of events, such as arrhythmias
\cite{baumert2004forecasting}. Unlike Jenssen-Shannon entropy, the
range of the compression entropy will vary between 0 (lower, or worse
compression rate) and 1 (no compression).

>>>>

In order to have enough data to perform more analysis on it, a new
experiment was performed along several days with, eventually, several
hundreds of persons participating on it. It was announced by several
popular Twitter figures and found its way into Reddit. The number of
PUTs per minute are shown in \ref{fig:minute}. Usually, sudden peaks in them
are due to new announcements in social networks, usually. This is one
of the problems with this kind of volunteer computing systems: they
feed on the continuous influx of new users; however, this can be
automatized and also encouraged, resulting, as shown, in that once enough users have
participated it is sometimes easier to find new ones.

The dot color in Figure \ref{fig:minute} corresponds to the {\em ratio} or, as indicated above, the actual
number of contributing PUTs, those that have not been discarded due to
repeated sending by clients or (briefly) belonging to the previous
instance of the experiment. It reveals that, in some cases where the
amount of PUTs really increases, they are actually not contributing so
much, while light dots, corresponding to a ratio close to 1, usually
stay in the lowest part of the graphic. 
%
\begin{figure}[ht!b]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/entropy-1}

@@

This is interesting in the sense that it indicates that there might be
something more to performance than just the number of volunteers
contributing. Therefore, in this experiment we include an additional measure:
user-contribution entropy, which is measured by computing the
compression entropy of every user contribution for the whole
experiment.  This is computed converting the sequence of the number of
PUTs into a string and then compressing it using {\tt Zlib}, a
standard compression library. Since the compression rate is related to
the randomness of the sequence, a higher compression rate will
correspond to an experiment with a low entropy, while a lower
compression rate will indicate that there has been a certain amount of
unexpected changes during the experiment. Although less popular than
Jenssen-Shannon entropy, this way of measuring it is widely used
\cite{ornstein1993entropy} in case where we want to compute the
entropy of sequences of events, such as arrhythmias
\cite{baumert2004forecasting}. Unlike Jenssen-Shannon entropy, the
range of the compression entropy will vary between 0 (lower, or worse
compression rate) and 1 (no compression).
